\section*{$IP$ and $NP$}
Claim:
$NP\subseteq IP$.\\
Proof: let $L\in NP$.
There exists some $NP$ relation $R$ for $L$, with an efficient algorithm $M_R$ which decides it.\\
Now define an $IP$ protocol:\\
\begin{itemize}
    \item Both $P$ and $V$ get $x$.
    \item If $x\in L$ P find $y$ s.t. $(x,y)\in R$, and send it to $V$. Otherwise send $\epsilon$.
    \item $V$ checks if $(x,y)\in R$ by running $M_R$ (known to be efficient) and accepts iff $M(x,y)$ accepts.
\end{itemize}
\begin{enumerate}
    \item Completeness: If $x\in L$, such $y$ must exist ($NP$ definition) thus $P$ will find it, and $V$ will have $(x,y)\in R$ so $M_R$ and $V$ will accept.
    \item Soundness: If $x\notin L$, there is no $y$ which such that $(x,y)\in R$ so no matter what any $P^*$ sends - $M_R(x,y)$ rejects and so $V$ rejects too.
 \end{enumerate}

\section*{Similar Proof Systems}
\subsection*{Arthur-Merlin - $AM$}
\begin{itemize}
    \item Both parties get some input $x$.
    \item Arthur sends Merlin some randomized $\alpha$.
    \item Merlin sends back some $\beta$.
    \item Arthur accepets according to some $PPT$ algorithm which is a function of $x,\alpha$ and $\beta$ (usually denoted $A(x,\alpha,\beta)$).
\end{itemize}

\subsection*{Merlin-Arthur - $MA$}
\begin{itemize}
    \item Both parties get input $x$.
    \item Merlin sends $\beta$ to Arthur.
    \item Arthur generates some random value $\alpha$.
    \item Arthur accepts according to some $PPT$ algorithm which is a function of $x,\alpha,\beta$.
\end{itemize}

Theorem: $MA\subseteq AM$.\\
Proof: Let $L\in MA$.
WLOG (without loss of generality), $L$ has a $MA$ protocol with perfect completeness (we will come back to this assumption later in the course).\\
Denote by $p(n)$ the length $\beta$ ($|\beta|\leq p(n)$).\\

Using repetition we can get to any protocol with perfect completeness and a soundness error of $2^{-p(n)-1}$ (as seen in lecture).\\
Sketching the repeated protocol would look like:
\begin{itemize}
    \item $M'$ sends $\beta$ to $A'$
    \item $A'$ sends back a list of $\alpha$ values (as many as there are repetitions).
    \item $A'$ decides wether to accept.
\end{itemize}
This is because there is not reason for the prover's proof ($\beta$) to change due to different sampling of $\alpha$, so it is always the same and can be sent once. So the length of Merlin's message does not change in the repeating protocol.\\

Now consider the same $M',A'$ protocol but where $A'$ sends the aggregated $\alpha$ before $M'$ sends $\beta$.

Claim: This new protocol is $AM$.
Proof:
\begin{enumerate}
    \item Completeness: $\forall x\in L, M'$ sends the same $\beta$ without looking at $\alpha$:
    \[Pr[(M',A)(x)=1]=Pr[A(x,\alpha,\beta)=1]=1\]
    \item Soundness: Let $x\notin L$, fix $M^*$.
    Consider:
    \[
        Pr[(M^*,A')(x)=1]
        =Pr[\exists\beta\in\{0,1\}^p: A'(x,\alpha,\beta)=1]
    \]\[
        =\cup_{\beta\in\{0,1\}^p} Pr[A'(x,\alpha,\beta)=1]
        \leq_{UB} 2^p2^{-(p+1)}=\frac{1}{2}
    \]
    Note: $UB$ denotes Union Bound.
\end{enumerate}
